% LaTeX resume using res.cls
\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\setlength{\topmargin}{-0.6in}  % Start text higher on the page
\setlength{\textheight}{9.8in}  % increase textheight to fit more on a page
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header
\usepackage{fancyhdr}  % use fancyhdr package to get 2-line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\lhead{\hspace*{-\sectionwidth}Brenda Baud} % force lhead all the way left
\rhead{Page \thepage}  % put page number at right
\cfoot{}  % the footer is empty
\pagestyle{fancy} % set pagestyle for the document

\begin{document}
\thispagestyle{empty} % this page does not have a header
\name{Andrew Kryczka}

\begin{resume}
\section{Education}
\vspace{0.1in}

{\bf University of Illinois at Urbana-Champaign College of Engineering:} B.S. with Highest Honors in Computer Science, May 2013.

{\bf National University of Singapore School of Computing:} Non-graduating Exchange Program, Fall 2011.

\section{Honors}
\vspace{0.1in}

{\bf Bronze Tablet/University Honors:} GPA in top 3\% of College of Engineering.

{\bf James Scholar:} Completed additional courses and group projects beyond what is required for graduation in Department of
Computer Science. Focused on systems and networking.

{\bf CS414 (Multimedia Systems) Best Project Award:} Member of team that developed group video chat application, which won class competition.

\section{Skills}
\vspace{0.1in}
C,
C++,
Python,
Java,
Scala,
Bash,
Network Configuration/Automation,
Distributed Systems,
Linux Kernel.

\section{Experience}
\vspace{0.1in}
    {\bf Software Engineer at Facebook,} Net Systems team (May 2014 -- present):
    \begin{itemize}
        \item Built configuration monitoring system.
    \end{itemize}

    {\bf Software Development Engineer at Amazon,} EC2 Networking team (July 2013 -- April 2014):
    \begin{itemize}
        \item Developed and maintained various network services (mostly C++) that run in Xen's dom0.
    \end{itemize}

    {\bf Undergraduate Researcher at UIUC:} Multimedia, Operating Systems, and Networking (MONET) research group (May
    2011 -- July 2013):
    \begin{itemize}
        \item Bachelor's thesis: ``Audio-visual Skew Detection and Correction in Multi-party Video Conferencing
            Applications.''
        \item Presented posters in two undergraduate research symposia.
        \item Information Trust Institute internship (Summer 2011).
    \end{itemize}

    {\bf Software Development Engineer Intern at Amazon,} AWS CloudFormation team (May 2012 -- August 2012):
    \begin{itemize}
        \item Developed a special-purpose test automation framework written in Java. It supports running tests on a
            Hudson continuous
    integration server and presents the results graphically.
        \item Contributed to new feature design and implementation using Java, Spring Framework, and APIs of various AWS services.
    \end{itemize}

\section{Publications}
\vspace{0.1in}

\underline{Andrew Kryczka}; Ahsan Arefin; Klara Nahrstedt, ``AvCloak: A Tool for Black Box Latency Measurements in Video
Conferencing Applications,'' IEEE International Symposium on Multimedia (Dec. 2013; acceptance rate 24\%).

Ke Liang; Beomjoo Seo; \underline{Andrew Kryczka}; Roger Zimmermann, ``IDM: An Indirect Dissemination Mechanism for Spatial Voice
Interaction in Networked Virtual Environments,'' IEEE Transactions on Parallel and Distributed Systems (Feb. 2013).
\end{resume}
\end{document}
